### 2025-02-22 paper-en.tex
Change citations

\begin{document}

@@

Many modern algorithms of data encoding use bipartite graphs with specific properties for error correction during data transmission over noise channels, e.g. Low Density Parity Check Codes \cite{LDPC}.

Methods of construction for such bipartite graphs are divided in two main categories: methods, based on random permutations of different graphs, e.g. brute-force search \cite{bruteforce} of pseudo-random permutation of matrices \cite{gallager}; and structured methods which build graphs based on fixed predefined structure, e.g. methods that use protographs \cite{protographs}.

@@

% ??

@@

% 13
\bibitem{quantum_error_correction}
G. Zémor, “On Cayley Graphs, Surface Codes, and the Limits of Homological Coding for Quantum Error Correction”
% https://www.researchgate.net/publication/220776025_On_Cayley_Graphs_Surface_Codes_and_the_Limits_of_Homological_Coding_for_Quantum_Error_Correction

% 14
\bibitem{vasic_combinatorial_construction}
B. Vasic, Combinatorial Constructions of Low-Density Parity-Check Codes for Iterative Decoding
% https://repository.arizona.edu/bitstream/handle/10150/641965/Combinatorial%20Constructions%20of%20Low-DensityParity-Check%20Codes%20for%20Iterative%20Decoding.pdf;jsessionid=9F016719B821C7D7CEBB9C48D7B37CB1?sequence=1

@@

>>>>

\begin{document}
\shorttitle{Metagraph approach for construction of an (m, n)-regular bipartite graph with a given girth}

@@

Many modern algorithms of data encoding use bipartite graphs with specific properties for error correction during data transmission over noise channels, e.g. Low Density Parity Check Codes \cite{johnson} \cite{ldpc_encoding}.

% Нужна ли цитата для переборного алгоритма, а то она потерялась
Methods of construction for such bipartite graphs are divided in two main categories: methods, based on random permutations of different graphs, e.g. brute-force search of pseudo-random permutation of matrices \cite{gallager}; and structured methods which build graphs based on fixed predefined structure, e.g. methods that use protographs \cite{protographs}. As well as various other methods \cite{margulis_construction} \cite{margulis_critique} \cite{imrich_construction} \cite{algebraic_aproach_to_sc_ldpc} \cite{lifts_of_graphs} \cite{vasic_combinatorial_construction} \cite{Kim2002ExplicitCO}.
% Разбить цитаты на группы: матричные/графовые отдельно

@@

@@

% 13
\bibitem{vasic_combinatorial_construction}
B. Vasic, Combinatorial Constructions of Low-Density Parity-Check Codes for Iterative Decoding
% https://repository.arizona.edu/bitstream/handle/10150/641965/Combinatorial%20Constructions%20of%20Low-DensityParity-Check%20Codes%20for%20Iterative%20Decoding.pdf;jsessionid=9F016719B821C7D7CEBB9C48D7B37CB1?sequence=1

%14
\bibitem{Kim2002ExplicitCO}
Jon-Lark Kim, Uri N. Peled. Irina G. Perepelitsa. Vera Pless, Explicit Construction of Families of LDPC Codes with Girth at Least Six, 2002
%https://homepages.math.uic.edu/~pless/preprint/allerton.pdf

@@

% 13

% Слишком общо, но можно по ссылкам пройтись
% \bibitem{quantum_error_correction}
% G. Zémor, “On Cayley Graphs, Surface Codes, and the Limits of Homological Coding for Quantum Error Correction”
% https://www.researchgate.net/publication/220776025_On_Cayley_Graphs_Surface_Codes_and_the_Limits_of_Homological_Coding_for_Quantum_Error_Correction
